Trends in Top 10 Causes of Death in Ontario

### 2024-03-17 paper/paper.qmd
Paper is unorganized and I can't figure out why

# Model
The model used to simulate, analyse, and predict the next five years of mortality data for the top ten causes of death in Ontario was produced using the rstanarm package and the stan_glm function. Taking advice from @rohan in his book Telling Stories With Data, we set out to fit our data to a negative binomial distribution. [INSERT FORMULA FOR NEGATIVE BINOMIAL PMF]. We regressed total deaths for each cause against cause of death dependent on the year. We used the negative binomial distribution because our data has a variance far exceeding the mean. [@tbl-min-max]. We also specify a log link function because as we are dealing with number of deaths, any negative value as a result of the model will not be telling of the real world. In this way using the log link function the predictions are always positive.

@@

```{r}
#| label: fig-model-one
#| fig-cap: "Summary of the negative binomal fitted model."
#| eval: true
#| echo: false
#| message: false
#| warning: false

summary(cause_of_death_ontario_neg_binomial)
```

@@

```
```{r}
#| label: fig-model-three
#| fig-cap: "Posterior prediction check for the negative binomial (left) and poisson (right) models."
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| layout-ncol: 2

>>>>

# Model
The model used to simulate, analyse, and predict the next five years of mortality data for the top ten causes of death in Ontario was produced using the rstanarm package and the stan_glm function. Taking advice from @rohan in his book Telling Stories With Data, we set out to fit our data to a negative binomial distribution. We regressed total deaths for each cause against cause of death dependent on the year. We used the negative binomial distribution because our data has a variance far exceeding the mean. [@tbl-min-max]. We also specify a log link function because as we are dealing with number of deaths, any negative value as a result of the model will not be telling of the real world. In this way using the log link function the predictions are always positive.

@@

@@

```{r}
#| label: fig-model-three
#| fig-cap: "Posterior prediction check for the negative binomial (left) and poisson (right) models."
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| layout-ncol: 2
